---
title: "Some plots"
author: "Hunter Ratliff, @HunterRatliff1"
date: "February 4, 2016"
output: ioslides_presentation
---

```{r, include=FALSE}
require(dplyr)
require(ggplot2)
require(ggthemes)
require(lubridate)

Numbers <- readRDS("Datasets/Numbers.RDS")
Numbers.melt <- readRDS("Datasets/Numbers_melt.RDS")
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Density Plots - Number of Dogs

```{r, echo=FALSE}
df %>% 
  filter(Timestamp<ymd("2016-03-01")) %>%
  mutate(
    Month = month(Timestamp, label = T),
    Year  = factor(year(Timestamp))) %>% 
  ggplot(aes(fill=Year)) + 
  
  geom_density(aes(x=Dogs.in.ICU), alpha=0.65) + 
  
  theme_fivethirtyeight() + 
  theme(axis.title=element_text(), axis.title.y=element_text(angle=90)) +
  scale_fill_stata() +
  
  labs(x="Number of Dogs") + facet_wrap("Month") 
```

## Boxplots - Number of Dogs

```{r}
df %>% 
  filter(Timestamp<ymd("2016-03-01")) %>%
  mutate(
    Month = month(Timestamp, label = T),
    Year  = factor(year(Timestamp))) %>% 
  ggplot(aes(fill=Year)) + 
  
  geom_boxplot(aes(x=factor(" "), y=Dogs.in.ICU)) +
  
  theme_fivethirtyeight() + 
  theme(axis.title=element_text(), axis.title.y=element_text(angle=90)) +
  scale_fill_stata() +
  
  labs(x="", y="Number of Dogs") + facet_wrap("Month", nrow = 2) 
```

# Scatter Plot - Dogs in ICU vs Shift Time

```{r}
df %>% ggplot() + 
  geom_jitter(aes(x=Shift.Time, y=Dogs.in.ICU, color=factor(year(Timestamp))), alpha=0.5) +
  theme_fivethirtyeight() + 
  theme(axis.title=element_text(), axis.title.y=element_text(angle=90)) +
  scale_color_stata(name="Year") +
  labs(x="Shift Time", y="Dogs in ICU")
```

```{r}
df %>% ggplot() + 
  geom_jitter(aes(x=Shift.Time * Count_Vols, y=Dogs.in.ICU, color=factor(year(Timestamp))), alpha=0.5) +
  theme_fivethirtyeight() + 
  theme(axis.title=element_text(), axis.title.y=element_text(angle=90)) +
  scale_color_stata(name="Year") +
  labs(x="ShiftTime x NumberOfVols", y="Dogs in ICU")
```

```{r}
df %>% ggplot(aes(x=Timestamp)) + 
  # geom_jitter(aes(y=60*Shift.Time/Dogs.in.ICU)) +
  # geom_smooth(aes(y=60*Shift.Time/Dogs.in.ICU)) +
  geom_smooth(aes(y=Count_Crt/Dogs.in.ICU)) +
  theme_fivethirtyeight() + 
  theme(axis.title=element_text(), axis.title.y=element_text(angle=90)) +
  scale_color_stata(name="Year") +
  labs(x="Shift Time", y="Dogs in ICU")
```

```{r}
df %>% lm(data=., Shift.Time~Dogs.in.ICU+Count_Vols) %>% summary()
```

```{r}
# Numbers %>%
#   mutate(
#     Dogs = Dogs.Crt+Dogs.Int+Dogs.Wel,
#     pCrt = Dogs.Crt/Dogs,
#     pInt = Dogs.Int/Dogs,
#     pWel = Dogs.Wel/Dogs) %>%
#   select(-Dogs.Crt, -Dogs.Int, -Dogs.Wel) %>%
#   # group_by(week = week(Date)) %>%
#   ggplot(aes(x=as.Date(Date))) + 
#   geom_smooth(aes(y=pCrt))
```

```{r}
Numbers.melt %>%
  mutate(Year = year(Date)) %>%
  ggplot(aes(x=yday(Date), y=All, color=Year)) + geom_smooth() #+ facet_wrap("Year")
  
```

## How Long Does The Shift Take?

```{r, echo=FALSE}
Numbers %>%
  ggplot(aes(x=as.Date(Date))) + 
  geom_jitter(aes(y=Durt.Shft, color=month(Date,label = T, abbr = T)), alpha=0.5) +
  geom_smooth(aes(y=Durt.Shft), color="red") + 
  scale_color_discrete(name="") + #guides(color=F) +
  guides(color=guide_legend(nrow=2)) +
  scale_x_date(date_breaks = "3 months", date_labels = "%b '%y") +
  labs(title="Duration of Parvo Shifts Over Time (Hours)\nColored By Month") +
  theme_fivethirtyeight()
```

## Slide with Plot

```{r, echo=FALSE}
Numbers.melt %>%
  filter(Count>0) %>%
  ggplot(aes(x=Count, y=Vols.Num*Durt.Shft)) + 
  # geom_jitter(aes(color=Status), alpha=0.5) +
  geom_violin(aes(fill=Status)) +
  # geom_smooth(aes(y=Time.Hours), color="red") + 
  labs(title="Duration of Parvo Shifts Over Time (Hours)\nColored By Month") +
  theme_hc()
```

## Slide with Plot

```{r, echo=FALSE}
readRDS("Datasets/Numbers_melt.RDS") %>%
  filter(year(Date.Time)==2015) %>%
  group_by(Month=floor_date(Date.Time, "month"), Status) %>% 
  summarise(Count=median(Count, T)) %>%
  ggplot(aes(x=Month, y=Count, fill=Status)) + 
  geom_bar(stat="identity", position = "dodge") + 
  theme_fivethirtyeight()

```